Preliminary Thesis Defence

### 2014-01-05 south-africa.tex
add more on evolution to results section

The last results is especially surprising,
considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
and roughtly half of the estimates of the \textbf{BMIZ} estimations.

@@

% DROP IN FEMALE RECIPIENTS, REMAIN LEVEL FOR MEN

\begin{table}[ht!]
\centering
\caption{Households with and without Male Pension Recipients}
\label{sa:ta:hmr}
    \begin{tabular}{l|rrrr}
    \hline
    Year              & 2008   & 2012   & 2013   & Overall \\
    \hline
    Male Recipient    & 612    & 595    & 623    & 1830    \\
    No Male Recipient & 6121   & 6138   & 6110   & 18369   \\
    Ratio of Male Recipients & 0.0909 & 0.0884 & 0.0925 & 0.0906  \\
    \end{tabular}
\end{table}

\begin{table}[ht!]
\centering
\caption{Households with and without Female Pension Recipients}
\label{sa:ta:fmr}
    \begin{tabular}{l|rrrr}
    \hline
    Year                & 2008   & 2012   & 2013   & Overall \\
    \hline
    Female Recipient    & 1637   & 1498   & 1509   & 4644    \\
    No Female Recipient & 5096   & 5235   & 5224   & 15555   \\
    Ratio               & 0.2431 & 0.2225 & 0.2241 & 0.2299  \\
    \end{tabular}
\end{table}

@@

% ASSUMPTIONS

% LIMITATIONS

% ROBUSTNESS

% RECOMMENDATIONS

>>>>

The last result is surprising,
considering that the coefficient estimates for \textbf{w\_spen\_m} in the \textbf{WHZ} estimations are all similar to each other,
and roughtly half of the estimates of the \textbf{BMIZ} estimations.

@@

Regarding the negative effect of the expansionary policy change, we need to further disseminate the change in the independent variables.
\autoref{sa:ta:hmr} and \autoref{sa:ta:hfr} describe the evolution of the number of children living in a household with a pension recipient.
We observe a substantial drop in both children living with male and female pension recipients.
The change for the number of children living in the same household as a male pension recipient is from 612 children in 2008 to 595 children in 2012. A drop of 17 or -2.79 percent.
However, if we compare the number of children living in the same household as a male pension recipient for the year 2013,
the results are quite different.
In the year 2013 we observe 623 children living with a male pension recipient, a rise of 1.8 percent vis-a-vis the year 2008.
When comparing the number of children living in the same household as a female pension recipient, we see a different picture.
In 2008 we observe 1637 children living with a female pension recipient,
and in the year 2012 we observe a number of 1498, a drop of 8.49 percent.
In the year 2013 we observe 1509 children living with female recipients in 2013,
a drop of 8.48 oercent vis-a-vis 2008.
We thus observe a drop in both the number of children living with male recipients,
of children living with female recipients between the years 2008 and 2012.
However, for male recipients the number rises to above 2008 levels in 2013,
where as the number for female recipients remains around the lower 2012 levels.

We thus observe a drop even in the number of children living with female pension recipients,
despite the fact that female pension recipients were unaffected by the policy change.

One of the reason for this drop in life expectancy in South Africa.
 % Include graph
The predominant reason for the this drop in life expectancy is taken to be HIV/AIDS.
% stats of people over 65.

\begin{table}[ht!]
\centering
\caption{Children in Households with and without Male Pension Recipients}
\label{sa:ta:hmr}
    \begin{tabular}{l|rrrr}
    \hline
    Year              & 2008   & 2012   & 2013   & Overall \\
    \hline
    Male Recipient    & 612    & 595    & 623    & 1830    \\
    No Male Recipient & 6121   & 6138   & 6110   & 18369   \\
    Ratio of Male Recipients & 0.0909 & 0.0884 & 0.0925 & 0.0906  \\
    \end{tabular}
\end{table}

\begin{table}[ht!]
\centering
\caption{Children in Households with and without Female Pension Recipients}
\label{sa:ta:hfr}
    \begin{tabular}{l|rrrr}
    \hline
    Year                & 2008   & 2012   & 2013   & Overall \\
    \hline
    Female Recipient    & 1637   & 1498   & 1509   & 4644    \\
    No Female Recipient & 5096   & 5235   & 5224   & 15555   \\
    Ratio               & 0.2431 & 0.2225 & 0.2241 & 0.2299  \\
    \end{tabular}
\end{table}

@@

% ASSUMPTIONS
% level effects

% LIMITATIONS
% simultanuous movement in recipient numbers.

% ROBUSTNESS
% questionable regarding the levelness.

% CONCLUSIONS
% which hold? what do we think?

% RECOMMENDATIONS
% estimate using by weighting the drop for women with life exp. evolution, and male also
% or use the drop for women (unaffected) to scale men and women back to 2008 levels.
